Copykat CNV results exploration for `r params$sample_id`

### 2024-10-15 analyses/cell-type-wilms-tumor-06/notebook_template/05_copykat_exploration.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook_template/05_copykat_exploration.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

`CopyKAT` was run using the `copyKAT.R` script with and without a normal reference, using either an euclidean or statistical (spearman) method to calculate distance in `copyKAT`.

>>>>

`CopyKAT` was run using the `05_copyKAT.R` script using either an euclidean or statistical (spearman) method to calculate distance in `copyKAT`. 
`CopyKAT` was run with and without a normal reference.
Immune and endothelial cells as identified by label transfer were used as the references cells where applicable.
